---
title: "men.rmd"
author: "Gabriela Pat"
date: "May 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
sex <- filter(avast,sex == "M")
```

# Introduction

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!



<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->



# Methods
 
 
We used barcharts, chi-squared test, and fisher tests to analyze the effectiveness of this drug across the board. For this section we will be using men only as a test subject.
 
 
 
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

 

#Results

Looking at the results from barcharts, chi-squared curve test, and fisher test it shows that the treatment for infected Men with aids is the better numbers. The treatment for Men infected with aids taking the placebo is the highest. In addition, the Men not infected with aids and taking the drugs, and the Men not infected and taking the placebo is close to each other, but still is higher than the Men infected with aids and taking the drugs, therefore we come to the conclusion that these two treatments didn't work either.


<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


## Descriptive Results
We look at the numbers from the barchart and discoverd that the only treatment that worked was the Men infected with aids and taking the drugs. The Men that used the treatment that is infected with aids and taking the placebo was the hightest therefore, this treatment was not working. Also the Men that is not infected with aids and taking the drugs, then the Men not infected with aids and taking the placebo were very close visually and they had the second and third hightest numbers showing us that these treatment didn't work either.


```{r}
trialtbl=xtabs(~infected+treatment,data=sex)
```

### Graphical Descriptive Results

The bar chart results show that the men infected with aids taking the drug treatment have lower results than the men who are infected with aids taking the placebo treatment. While the men not infected with aids that are taking the drug treatment and the men not infected with aids who are taking the placebo treatment seem to have almost the same results except that the drug treatment is slightly higher. 


<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(trialtbl,type = "percent")
```



### Numerical Descriptive Results

This we see that only the Infected with aids and taking the drugs is working. The infected with aids and taking the placebo is not not working and has the highest numbers. The none infected with taking the drug and the none infected placebo is almost the same, slightly different.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
colPerc(trialtbl)
```

In the column for treatment we see that both Men groups that's infected with aid and taking the drugs and the placebo have low numbers and both Men groups with the none infected aids with drugs and the placebo have high numbers. 

```{r}
rowPerc(trialtbl)
```
The row results show that only the drug treatment worked on the men infected with aids. While the placebo with infected had higher results when compared to the Men who do not have aids, without being infected .

## Inferential Results

The Observed Counts of the treatment in Infected Men with aids taking the drugs is 213 and the placebo is 465. The none Infected Men with durgs is 4684 and with the placebo is 4613.The Counts Expected by Null with Infected Men with aids and taking the drugs is 4684. The none Infected Men with taking the placebo is 4613. The Counts Expected by Null that's Infected Men with aids and taking the drugs is 332.85. The Infected Men with aids taking the placebo is 345.15. The none Infected Men with drugs is 4564.15, and the none Infected Men taking the placebo is 4732.85. The Contributions to the chi-square statistic with the Infected Men with aids and taking the drugs is 43.15 and the Infected Men with aids taking the placebo is 41.52. Then, the non Infected Men taking the drugs is 3.15 and the none Infected Men taking the placebo is 3.03. The Chi-Square Statistic = 90.1943. The Degrees of Freedom of the table = 1. The P-Value = 0. Which means the p-values accepted the hypothesis is not null.


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(trialtbl, graph = TRUE)
```


```{r}
fisher.test(trialtbl)
```
The Fisher test is rejected because the p-value is < 2.2e-16 and we don't know the correct number thats less than. Our hypothesis on the fisher test is null, because the p-value is over 0.5.




# Discussion and Conclusion
We conclude, that our hypothesis is null and that looking at all the charts: chi-square curve, fisher test, barchart, the column and the row, which tells us the evidence of Men that is infected with aids and taking the drugs is the lowest and therefore, the treatment was working for those men. However, the Men infected with aids and taking the placebo had the hightest results that lets us know that the treatment wasn't working. Also, the Men not infected and taking the drugs and not infected and taking the placebo was very close and very close on all the numbers and on the barchart that lets us know these two in the treatment didn't work either.


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
