---
title: "women.rmd"
author: "Gabriela Pat"
date: "May 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
sex <- filter(avast,sex == "F")
```

# Introduction

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation.

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->



# Methods

We used barcharts, chi-squared test, and fisher tests to analyze the effectiveness of this drug across the board. For this section we will be using women only as a test subject.


<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

#Results

Looking at the results from barcharts, chi-squared curve test, and fisher test, the columns and rows which shows that the treatment for infected Women with aids and taking the drugs is the lowest number. The treatment for Women infected with aids taking the placebo is the highest. In addition, the Women not infected with aids and taking the drugs is the third highst, and the Women not infected and taking the placebo is second hightest. All of these results is not good


<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

We look at the numbers from the barchart and discoverd that the only treatment that is the highest for the Women infected with aids and taking the drugs. Then, the Women that used the treatment that is infected with aids and taking the placebo was the lowest. Also the Women that is not infected with aids and taking the drugs is the third highest, then the Women not infected with aids and taking the placebo is second highest.

```{r}
trialtbl=xtabs(~infected+treatment,data=sex)
```
### Graphical Descriptive Results

The barchart results show that the Women infected with aids and taking the drug treatment have the highest on the barchart results is not good wich is about 59%. The Women who are infected with aids taking the placebo treatment that has the lower results, which is not good wich is about 39%. While the Women not infected with aids taking the drug treatment is the third highest with about 48%, and then, Women fected with aids who are taking the placebo treatment is the second highest result with is about 50%.


<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(trialtbl,type = "percent")
```
### Numerical Descriptive Results

This we see that the Women infected with aids and taking the drugs is the highest working with the numbers of 58.82. The Women that is infected with aids taking the placebo is the the lowest number of  41.18,the Women not infected with aids and taking the placebo is the sencond highest with 51.94, and Women not infected with drugs have the third highest number of 48.06.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->



```{r}
colPerc(trialtbl)
```
These columns show that the treatment for women who do have aids did work.  While the drug treatment on women without aids did not. The drug treatment on the women with aids was 3.69 and the placebo treatment on women with aids was 2.42.work. The drug treatment on women without aids was 96.31 and the placebo treatment on women without aids is 97.58.

 
 

```{r}
rowPerc(trialtbl)
```

These rows show that the the treatment for women who do have aids did not work. The drug treatment on the women with aids was 58.82 and the placebo treatment on women with aids was  41.18. The drug treatment on women without aids did not work either. The drug treatment on women without aids was  48.06 and the placebo treatment on women without aids is 51.94.Both did not give good results. All for have no good results.


## Inferential Results


The Observed Counts of the treatment in Infected with aids Women taking the drugs is 210 and the placebo is 147. The none Infected Women with durgs is 5484 and with the placebo is 5927. The Counts Expected by Null, infected Women with aids and taking the drugs is 172.74. The Infected Women taking the placebo is 184.26. The Counts Expected by Null that's not infected Women with aids and taking the drugs is 5521.26. The not infected Women with aids taking the placebo is 5889.74.  The Contributions to the chi-square statistic Women infected with aids and taking the drugs is 8.04 and the Infected with aids Women taking the placebo is  7.54. Then, the not infected with aids Women taking the drugs is 0.25 and the not infected with aids Women taking the placebo is 0.24. The Chi-Square Statistic = 15.6339. The Degrees of Freedom of the table = 1. The P-Value = 1e-04. Which means the p-values accepted the hypothesis is not null in these results.


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(trialtbl, graph = TRUE)
```

The chi-squared  test gave us a p-value of  1e-04 
which shows that we shall reject the null hypothesis.

```{r}
fisher.test(trialtbl)
```


The Fisher test is rejected because the p-value is < 6.596e-05 and we know the correct number is more than the p-value should be, therefore, our hypothesis on the fisher test is null and the alternative hypothesis: true odds ratio is not equal to 1. Then, 95 percent confidence interval:  1.240408 1.925729

# Discussion and Conclusion

We conclude, that our hypothesis is null and that looking at all the charts: chi-square curve, fisher test, barchart, the columns and the rows, which tells us the evidence of Women that is infected with aids and taking the drugs is the highest and therefore, the treatment wasn't working for the Women. Also, the Women infected with aids and taking the placebo had the lowest results that lets us know that the treatment wasn't working. Also, the Women not infected and taking the drugs and not infected and taking the placebo was slightly diferent numbers that lets us know these two in the treatment didn't work either. None of these were good conclusions.


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We conclude, that our hypothesis is null and that looking at all the charts: chi-square curve, fisher test, barchart, the column and the row, which tells us the evidence of Women that is infected with aids and taking the drugs is the highest and therefore, the treatment wasn't working for the Women. Also, the Women infected with aids and taking the placebo had the lowest results this still was too high so, we know that the treatment wasn't working. Also, the Women not infected and taking the drugs and not infected and taking the placebo was slightly diferent numbers that lets us know these two in the treatment didn't work either. None of these were good conclusions.






