---
title: "women.rmd"
author: "Gabriela Pat"
date: "May 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
sex <- filter(avast,sex == "F")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

I will use barcharts, chi-squared test, and fisher tests to analyze the effectiveness of this drug across the board. For this section I will be using women only as a test subject.

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

Looking at the results from barcharts, chi-squared test, and fisher test it shows that the treatments with and without the drug are not working for women. 

## Descriptive Results

```{r}
trialtbl=xtabs(~infected+treatment,data=sex)
```

I am observing how the drug treatment and the placebo treatments are working on women. I will be looking at whether the treatments are good or bad on women. 

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(trialtbl,type = "percent")
```

The bar chart proves that it is not working for women.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

These columns show that the treatment for women who do have aids did work.  While the drug treatment on women without aids did not The drug treatment on the women with aids was 3.69 and the placebo treatment on women with aids was 2.42.work. The drug treatment on women without aids was 96.31 and the placebo treatment on women without aids is 97.58.

```{r}
colPerc(trialtbl)
```

These rows show that the the treatment for women who do have aids did not work. The drug treatment on the women with aids was 58.82 and the placebo treatment on women with aids was  41.18. The drug treatment on women without aids did not work either. The drug treatment on women without aids was  48.06 and the placebo treatment on women without aids is 51.94.Both did not give good results. 
 

```{r}
rowPerc(trialtbl)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(trialtbl, graph = TRUE)
```

The chi-squared  test gave us a p-value of  1e-04 
which shows that we shall reject the null hypothesis.

```{r}
fisher.test(trialtbl)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Looking back at all the results that the barcharts, chi-squared tests, and fisher tests gave us on all the women, I can conclude that the both the drug and placebo treatments did not work on women. The placebo 